%!TEX TS-program = xelatex
\documentclass[a4paper]{friggeri-cv}

\begin{document}

\header{Émilien }{ BAI}
       {Blockchain / Fullstack Engineer}


% In the aside, each new line forces a line break
\begin{aside}
  \section{About}
    Augustenstraße 67
    Whg. 27
    80 333 München
    Deutschland
    ~
    \href{mailto:contact@emilienbai.fr}{contact@emilienbai.fr}
    +33 (0)6 04 42 50 18
    ~
    Driving License
    International Mobility
  \section{Languages}
  	French Mother Tongue
	English Advanced
	(TOEIC 970/990)
	German Intermediate (B1)
	Swedish Notions	
  \section{Programming}
    Python, Typescript, 
	Solodity, NodeJs,    
    Java, C\#, C/C++, 
    Shell, SQL, OpenGL (basics)
    Arduino
  \section{Diverse}
    Linux, Windows, 
    Eclipse, Intellij Idea
    NetBeans, Android Studio, 
    Visual Studio,
    \LaTeX, Git, SVN     
\end{aside}

\section{Education}

\begin{entrylist}
 \entry
    {2014..17}
    {Computer Science and Engineering student}
    {INSA Lyon}
    {Theatrical technician option }
   \entry 
	{2016..17}
	{Exchange student}
	{Luleå University of Technology}
	{Computer science program and Swedish courses}
  \entry
    {2012..14}
    {Undergraduate program in sciences engineering}
    {INSA Lyon}
    {Theatrical technician option}
  \entry
    {2012}
    {French Baccalauréat S with honors}
    {Lycée Champagnat (69)}
    {Specialization in mathematics and physics}
\end{entrylist}

\section{Experiences}

\begin{entrylist}
\entry
{09 2017 - ...}
{3dTrust GmbH, München, DE}
{Blockchain / Fullstack Developer}
{\begin{myitemize}
\vspace{-12pt}
\item Active participation in the design of the Blockchain/smart-contracts architecture part of our application. This blockchain part is grafted on top of an existing application and aimed at securing and guaranteeing the consistency of sensitive data.
\item Development of a scheduling algorithm to automate production planning. This algorithm has been integrated in the final product, a production monitoring and management system oriented at additive manufacturing.  
\item Implementation of a link between the existing application and a newly created blockchain architecture.
\end{myitemize}
}

\entry
{02-06 2017}
{Luleå University of Technology, Luleå, SE}
{Research Intern}
{\begin{myitemize}
\vspace{-12pt}
\item Design and implementation of a reward system for collaborative care of elderly. The goal was to design from scratch a system to motivate potential volunteers to bring help to elderly people.
\item Development of a back-end based on smart-contracts using distributed ledger technologies and a mobile application as a blockchain ”wallet”. The use of a blockchain was a requirement in the internship subject. I developed my entire back-end using Burrow, the blockchain solution from Monax,a fork of Ethereum using Solidity as the smart contract development language.
\item Publication of a research paper in the conference proceedings of UBICOMM 2017 (Barcelona, November 2017).
\end{myitemize}
}

\entry
{05-08 2016}
{Foxstream, Vaulx-en-Velin, FR}
{Software Engineer Intern}
{\begin{myitemize}
\vspace{-12pt}
\item Update of Foxtool, software used for CCTV camera placement simulation.
\item Creation of cameras point of view 3D simulation using C\#, OpenTK and GLSL.
\item Refresh of the global architecture of the application by the inclusion of common design patterns in the existing version.
\item Refresh of FoxTool UX then GUI using Winform.
\end{myitemize}
}
\entry
{May 2016}
{INSA Lyon, FR}
{Group project "Potholess"}
{\begin{myitemize}
\vspace{-12pt}
\item Creation of a working prototype of an embedded system using sunspot sensors and a raspberry pi.
\item Automatic detection of roads imperfections (potholes) and data collection. Data is automatically sent to a server to be analyzed.
\item Entire development in a 10 days sprint with 5 other students.
\end{myitemize}
}
  \entry
    {06-08 2015}
    {XLR Project, Lyon, FR}
    {Software Engineer Intern}
	{\begin{myitemize}
\vspace{-12pt}
\item Entire development of a Java application from specifications to release.
\item Collection of analog signals with an Arduino board then conversion into MIDI and OSC messages to create interaction with most of the creative live software.
\item Integration with a drum set to create an interactive video installation.
\end{myitemize}    
}

\end{entrylist}

\section{Volunteer experience}
\begin{entrylist}
	\entry
	{2015-2016}
	{Commission de Gestion de la Rotonde (CGR)}
	{Vice president}
	{Management of the theater of the campus of "la Doua" : schedule, material park management, rentals.}
	\entry
	{2014-2016}
	{Festival Karnaval Humanitaire, logistic team}
	{Technician}
	{Light equipment research and gathering, assembly of the stage and the technical facilities during the festival.}
	\end{entrylist}
	
\section{Publications}
\subsection{International peer-reviewed conferences/proceedings}
{\textbf{ “A Reward System for Collaborative Care of Elderly based on Distributed Ledger Technologies”}}, 

{\textit {Emilien Bai and Kåre Synnes}}, {\small In the proceedings of the Eleventh International Conference on Mobile Ubiquitous Computing, Systems, Services and Technologies (UBICOMM), November 12-16, 2017, Barcelona, Spain , [ed] IARIA, ISSN: 2308-4278, ISBN: 978-1-61208-598-2}

\section{Interests}
Theatrical technician : lightning for theater plays, dance shows, sound technician for concerts.
Realization of short films. Amateur photographer.

\end{document}
